---
title: "ggKM"
author: Tingting Zhan
format: 
  html:
    page-layout: full
    html-math-method: katex
toc: true
toc-location: left
toc-depth: 4
toc-title: ''
editor: visual
vignette: >
  %\VignetteIndexEntry{intro}
  %\VignetteEngine{quarto::html}
  %\VignetteEncoding{UTF-8}
---

# Introduction

This vignette of package **`survival.tzh`** ([Github](https://github.com/tingtingzhan/survival.tzh), [RPubs](https://rpubs.com/tingtingzhan/VisualizeSimon2Stage)) documents `ggKM()`.

## Note to Users

Examples in this vignette require that the `search` path has

```{r}
#| message: false
library(survival.tzh)
library(ggplot2)
library(rpart)
library(patchwork)
```

```{r}
#| echo: false
#options(mc.cores = 1L) # for CRAN submission

theme_set(
  theme_bw(
    base_size = 11, 
    base_family = 'Arial Unicode MS', 
    base_line_size = 11/22, 
    base_rect_size = 11/22
  ) %+replace% 
    theme(
      axis.ticks = element_blank(), 
      #legend.background = element_blank(), 
      legend.background = element_rect(color = 'grey95'),
      #legend.key.spacing.y = unit(.015, units = 'npc'),
      legend.key.spacing.y = unit(.02, units = 'npc'),
      legend.key = element_blank(), 
      panel.background = element_blank(), 
      panel.border = element_blank(), 
      strip.background = element_blank(), 
      plot.background = element_blank(), 
      complete = TRUE
    )
)
```

## Terms and Abbreviations

| Term / Abbreviation | Description |
|--------------------------------------------|----------------------------|
| [`|>`](https://search.r-project.org/R/refmans/base/html/pipeOp.html) | Forward pipe operator introduced in `R` 4.1.0 |
| `$` | [Extract](https://search.r-project.org/R/refmans/base/html/Extract.html) parts of an object |
| [`binom`](https://search.r-project.org/R/refmans/stats/html/Binomial.html) | [Binomial](https://en.wikipedia.org/wiki/Binomial_distribution) density and distribution |
| `CRAN`, `R` | [The Comprehensive R Archive Network](https://cran.r-project.org) |
| [`class`](https://search.r-project.org/R/refmans/base/html/class.html) | Object class |
| [`flextable`](https://search.r-project.org/CRAN/refmans/flextable/html/flextable.html) | Flexible tables |
| `PASS` | Power Analysis & Sample Size, <https://www.ncss.com/software/pass/> |
| `PET` | Probability of early termination |
| [`ph2simon`](https://search.r-project.org/CRAN/refmans/clinfun/html/ph2simon.html) | Simon's 2-stage Phase II design |
| `S3`, `generic`, [`methods`](https://search.r-project.org/R/refmans/utils/html/methods.html) | `S3` object oriented system, [`UseMethod`](https://search.r-project.org/R/refmans/base/html/UseMethod.html); [`getS3method`](https://search.r-project.org/R/refmans/utils/html/getS3method.html); <https://adv-r.hadley.nz/s3.html> |
| `S4`, `generic`, `methods` | `S4` object oriented system, [`isS4`](https://search.r-project.org/R/refmans/base/html/isS4.html); [`setClass`](https://search.r-project.org/R/refmans/methods/html/setClass.html); [`getMethod`](https://search.r-project.org/R/refmans/methods/html/getMethod.html); <https://adv-r.hadley.nz/s4.html> |
| [`search`](https://search.r-project.org/R/refmans/base/html/search.html) | Search path |
| [`seed`](https://search.r-project.org/R/refmans/base/html/Random.html) | Random number generation seed |

# Data Example

```{r}
rotterdam2 = survival::rotterdam |> 
  within.data.frame(expr = {
    rtime = as.difftime(rtime, units = 'days')
    dtime = as.difftime(dtime, units = 'days')
    rfs = Surv(rtime, event = recur)
    os = Surv(dtime, event = death)
    units(rfs) = units(os) = 'years'
  })
```

# Kaplan-Meier Curves

```{r}
rotterdam2$os |> autoplot()
```

```{r}
ggKM(os ~ 1, data = rotterdam2)
```

```{r}
ggKM(os ~ size, data = rotterdam2)
```

```{r}
# fix: error
# ggKM(os ~ size, data = rotterdam2, times = c(5, 10))
```

```{r}
ggKM(os ~ size, data = rotterdam2, labels = letters[1:3])
```

```{r}
ggKM(os ~ size + I(age > 60), data = rotterdam2)
```

```{r}
rpart(os ~ age, data = rotterdam2, maxdepth = 2L, model = TRUE) |>
  ggKM()
```

## `subset_ggKM()`

```{r}
#| fig-width: 10
subset_ggKM(os ~ size, subset = list(
  All = TRUE, pre = (meno == 0), post = (meno == 1)
), data = rotterdam2) +
  plot_layout(ncol = 2L)
```

```{r}
#| fig-width: 10
id = quote(list(
  All = TRUE, pre = (meno == 0), post = (meno == 1)
))
subset_ggKM(os ~ size, subset = id, data = rotterdam2) +
  plot_layout(ncol = 2L)
```

## `m_ggKM()`

```{r}
#| fig-width: 10
m_ggKM(cbind(rfs, os) ~ chemo, data = rotterdam2)
```
